Generating Simulated Data

### 2021-04-09 docs/SimData.Rmd
id threshold lengths based on vonBk

  #vonBk tells you how many fine bins for fast growth
  # threshold cumprod of 0.05 to define last bin? tiny growth increment
  # use binopt up to this threshold?
  # plot(cumprod(rep(1, 160)*exp(-0.0386)), ylim=c(0,1), xlim=c(0,180)) #saithe
  # lines(cumprod(rep(1, 20)*exp(-1.4)), ylim=c(0,1), xlim=c(0,180)) #capelin
  # lines(cumprod(rep(1, 40)*exp(-0.163)), ylim=c(0,1), xlim=c(0,180)) #redfish
  # lines(cumprod(rep(1, 130)*exp(-0.344)), ylim=c(0,1), xlim=c(0,180)) #cod
  #low vonBK is doesn't asympote, divide length range equally into nbins?

>>>>

  #vonBk tells you how many fine bins for fast growth
  # threshold cumprod of 0.05 to define last bin? tiny growth increment
  # use binopt up to this threshold? 
  # plot(cumprod(rep(1, 160)*exp(-0.0386)), ylim=c(0,1), xlim=c(0,180)) #saithe
  # lines(cumprod(rep(1, 20)*exp(-1.4)), ylim=c(0,1), xlim=c(0,180)) #capelin
  # lines(cumprod(rep(1, 40)*exp(-0.163)), ylim=c(0,1), xlim=c(0,180)) #redfish
  # lines(cumprod(rep(1, 130)*exp(-0.344)), ylim=c(0,1), xlim=c(0,180)) #cod

  thresh <- 0.05
  which(cumprod(rep(1, Lmax)*exp(-vonBk)) < thresh) #gives lengths of fast growth

  #low vonBK is doesn't asympote, divide length range equally into nbins?
